Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-09-02 main_paper.tex
Changes in the discussion of CCF

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not.

>>>>

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not. Furthermore, \cite{CCF15} analyzes properties of
the proposed bias-corrected studentized statistics based on a fixed-$n$ calculation
 for standard errors and demonstrates through higher-order expansions that confidence intervals based on these
 statistics achieve superior coverage-error order relative to undersmoothing.
Additionally, they provide bandwidth choice procedures which are ``coverage-error optimal.''
